Introduce the topic of research and explain its academic and industrial context.

\begin{itemize}
    \item Establish the general subject area.
    \item Describe the broad foundations of your study -- provide adequate background for readers.
    \item Indicate the general scope of your project.
    \item Provide an overview of the sections that will appear in your proposal (optional).
    \item Engage the readers.
\end{itemize}

% -------------------------------------------------------------------------------------------------------------------

Pinpointing risk factors for firms and market dynamics is a multifaceted challenge.
Internal company data on operations can become entangled with external forces like economic shifts, making it difficult
to untangle the source of issues.
Further complicating matters is the vast amount of potentially relevant information.
Financial reports, news articles, and social media trends all hold valuable clues, but efficiently filtering this data
and extracting the key risk indicators is a hurdle.
This information overload makes it challenging to create a clear picture of potential risks and develop effective
mitigation strategies.

In recent years, the field of Natural Language Processing (NLP) has been experiencing a boom in interest across various
industries.
This surge is fueled by NLP's ability to unlock the vast potential of unstructured data, text that doesn't reside in
neat rows and columns like spreadsheets.
NLP tools can now analyse large amounts of information from social media posts, customer reviews, and even news
articles, extracting meaning and identifying trends that would be nearly impossible for humans to manage.
This newfound ability to understand and utilise the information we generate is transforming fields like finance.
Refer to ~\cite{Lee2024} and ~\cite{Li2023} for recent surveys about LLMs in finance and ~\cite{Zhao2024} for an overview
of applications and insights into how LLMs are revolutionizing finance.

Large language models (LLMs) offer a revolutionary approach to untangling the complexities of risk management.
By being adept at processing massive amounts of data, LLMs can delve into financial reports, news streams, and social
media chatter, summarizing the key points and identifying trends that might otherwise be lost in the information
overload.
This document summarization capability empowers businesses to gain a clearer understanding of potential risks, both
internal and external.
By analysing vast datasets and highlighting crucial details, LLMs can act as a powerful tool for risk identification,
paving the way for more proactive and effective risk mitigation strategies.


% ChatGPT and Large Language Models for Financial Assets Summary
% Principal Goal: The aim of this project is to explore adopting LLMs and ChatGPT for summarising firms financial
% fundamentals and assessing the prediction power of such summaries.
%
% A survey of more than 1,000 financial industry professionals indicate that it is challenging to recognize and
% understand major risks factors associated with firms and market dynamics and manually process such information
% is a significant challenge itself. Recent AI-driven LLMs provide revolutionary solutions to address such challenges,
% we aim to leverage bespoke finance LLMs with vast amount of online information and financial report data to enhance
% abrdn’s investment management process.  However, currently, large language models such as GPT-4, lack firm specific
% financial information and counting for firms’ relationships and sector based real-time summarization capability,
% which is a clear shortcoming for financial the financial industry who needs reliable risk factors analysis in
% real-time.  We aim to quantify firm fundamental information, and market news (positive, or negative) related to
% multiple dimensions of firms from global news archives over the last 20 years that can be traced to a particular
% country, sectors with focus on fixed income and equity markets.  This project aims to explore firm-based - risk
% factors are measured, hence unlocking the potential for significant improvements in the fields of finance investment
% management, and decision-making.
%
% The main focuses of this project are (i) develop financial documents summarization based on existing pretrained
% LLM models, which has the capability of providing essential summaries of firms historical and fundamental
% information. The project will explore the summarizes of (a) firms’ business activities, earnings; (b) growth
% potentials, key revenue drivers and industry recommendations etc;


% -------------------------------------------------------------------------------------------------------------------
\subsection{Problem Statement}\label{subsec:problem-statement}

\begin{itemize}
    \item Answer the question: "What is the gap that needs to be filled?"
    and/or "What is the problem that needs to be solved?"
    \item State the problem clearly early in a paragraph.
    \item Limit the variables you address in stating your problem.
    \item Consider bordering the problem as a question.
\end{itemize}

\subsection{Research Hypothesis and Objectives}\label{subsec:research-hypothesis-and-objectives}

Identify the overall aims of the project and the individual measurable objectives against which you would
wish the outcome of the work to be assessed.
Clearly spell out any research hypothesis you are following.

Include a justification (rationale) for the study.
Be clear about what your study will not address.


\subsection{Timeliness and Novelty}\label{subsec:timeliness-and-novelty}

Explain why the proposed research is of sufficient timeliness and novelty

\subsection{Significance}\label{subsec:significance}

The proposal should demonstrate the originality of your intended research.
You should therefore explain why your research is important
(for example, by explaining how your research builds on and adds to the current state of knowledge in the field or
by setting out reasons why it is timely to research your proposed topic) and providing details of any
immediate applications, including further research that might be done to build on your findings.

\subsection{Feasibility}\label{subsec:feasibility}

Comment on the feasibility of the research plans given its limited time frame and resources.
Outline your plans for a feasibility study before starting e.g.\ major implementation work.

\subsection{Beneficiaries}\label{subsec:beneficiaries}

Describe how the research will benefit other researchers in the field and in related disciplines.
What will be done to ensure that they can benefit?
